Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-23 ms.tex
efficiency tangle.

\newcommand{\Mdot}{\dot{M}}
\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\MdotEdd}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

@@

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddr}{10^{-4}}\right)^{0.9} & \eddr \lsim 10^{-4} \\
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
  0.1 \left(\frac{\eddr}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
  0.1 & \eddr \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6
in \citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. For $\eddr\gsim 0.1$, $\epsilon_{rad}$ should saturate
to 0.1, hence the fourth line. The third line is a power law which
connects $\epsilon_{\rm rad} (\eddr=0.01) = 0.026$ to $\epsilon_{\rm
  rad} (\eddr=0.1) = 0.1$.

Additionally, a large fraction of the $\dot{M}$ on large scales will
be driven out in outflows as the gas has some non-zero angular
momentum and a centrifugal barrier will stop it from accreting
\citet{Li+2013}. In the limit weak cooling appropriate for low
accretion rates the accretion rate on small scales will be of order
$\alpha \Mdot$.  Taking $epsilon=\alpha \epsilon_{\rm rad}$ for the
overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
equation~\eqref{eq:efficiency} we obtain {\bf AG note the change in
  the description of the efficiency},

\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 5.9\times 10^{-3} \eta_{0.02}^{0.12}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.09}
&, \text{core}\\ 2.1\times 10^{-3} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
We note that accretion is unlikely to be steady in cases where AGN
heating dominates, due to the inherent delay between black hole
feedback and the structure of the accretion flow on larger scales.
Equations (\ref{eq:MdotCa}), (\ref{eq:MdotC}) may nevertheless
represent characteristic average value for the accretion rate,
assuming a quasi-equilibrium state is achieved over many cycles.
%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
  (\alpha/0.1) \epsilon_{rad} (\eddr) $, where $\epsilon_{\rm rad}$ is
  given by equation~\eqref{eq:efficiency}.  Shown for comparison are
  the X-ray luminosities calculated for the maximum thermally-stable
  accretion rate ({\it dashed orange line}; eq.~[\ref{eq:Mdotmax}]);
  the SN Ia-regulated accretion rate ({\it dashed teal line};
  eq.~[\ref{eq:eddr_Ia}]), and the Compton heating-regulated accretion
  rate ({\it dashed pink line}; eq.~[\ref{eq:MdotCa}]), again all
  calculated for the average SFH corresponding to each SMBH mass.}
\end{figure*}

>>>>

\newcommand{\Mdot}{\dot{M}}
\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\eddrt}{\tilde{\dot{M}}/\dot{M}_{\rm Edd}}
\newcommand{\MdotEdd}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

@@

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddrt}{10^{-4}}\right)^{0.9} & \eddrt \lsim 10^{-4} \\
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddrt \lsim  10^{-4}\\
  0.1 \left(\frac{\eddrt}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddrt \lsim  0.1\\
  0.1 & \eddrt \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}

The first two lines are a piecewise power law fit designed to
approximately reproduce the solid line in Figure 6 in
\citet{Sharma+2007}, which assumes 33\% of the viscous dissipation
heats the electrons. For $\eddrt\gsim 0.1$, $\epsilon_{\rm rad}$
should saturate to 0.1, hence the fourth line. The third line is a
power law which connects $\epsilon_{\rm rad} (\eddrt=0.01) = 0.026$ to
$\epsilon_{\rm rad} (\eddrt=0.1) = 0.1$. The tildes are put in as a
reminder that the efficiency will depend on the small scale $\Mdot$
($\tilde{\dot{M}}$) which will in general be different from the large
scale $\Mdot$.

Additionally, a large fraction of the $\dot{M}$ on large scales will
be driven out in outflows as the gas has some non-zero angular
momentum and a centrifugal barrier will stop it from accreting
\citet{Li+2013}. In the limit weak cooling appropriate for low
accretion rates the accretion rate on small scales will be of order
$\alpha \Mdot$.  We take $\epsilon=\alpha \epsilon_{\rm rad}$ for the
overall efficiency with $\alpha=0.1$ and $\epsilon_{\rm rad}$ from
equation~\eqref{eq:efficiency}. This means that the bolometric
luminosity, $L=\epsilon \Mdot c^2=\alpha \epsilon_{\rm rad} (\alpha
\eddr) \Mdot c^2= \epsilon_{\rm rad} (\eddrt) \tilde{\dot{M}} c^2$, where
$\Mdot$ is mass inflow rate on large scales and $\tilde{\dot{M}}$ is
the mass inflow rate on small scales. Note that in evaluating the
efficiency one has to account for the $\alpha$ suppression in $\eddr$.
we obtain {\bf AG note the change in the description of the
  efficiency. Also, the alpha's kept tripping me up},

\begin{align}
\frac{\dot{M}_{C}}{\dot{M}_{\rm edd}} \approx 
\begin{cases} 6\times 10^{-3} \eta_{0.02}^{0.12}T_{\rm
C,9}^{-0.44}M_{\bullet,8}^{0.09}
&, \text{core}\\ 2\times 10^{-3} \eta_{0.02}^{0.17}T_{\rm
C,9}^{-0.4} M_{\bullet,8}^{0.08}
&, \text{cusp}.
  \end{cases}
  \label{eq:MdotC}
\end{align}
We note that accretion is unlikely to be steady in cases where AGN
heating dominates, due to the inherent delay between black hole
feedback and the structure of the accretion flow on larger scales.
Equations (\ref{eq:MdotCa}), (\ref{eq:MdotC}) may nevertheless
represent characteristic average value for the accretion rate,
assuming a quasi-equilibrium state is achieved over many cycles.
%{\bf  Total efficiency is 10 (mdot/MdotEdd). Everywhere.}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average nuclear X-ray luminosity, $\langle
  L_X \rangle = \epsilon_X \Mdot c^2$, as a function of SMBH mass.
  Green lines show our prediction in the case of heating due to the
  average SFH for galaxies corresponding to each black hole mass
  (Fig.~\ref{fig:bh_growth}), calculated using a power-law fit for the
  relationship $\Gamma(M_{\bullet})$ derived from the
  \citet{LauerFaber+:2007a} sample.  Shown for comparison are the
  measurements ({\it black stars}) and upper limits ({\it gray
    triangles}) for $L_X/L_{\rm edd}$ values, from the
  \citet{Miller+15} sample of early-type galaxies (a black line shows
  the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto
  M_{\bullet}^{\alpha}$, with $\alpha = -0.2$).  The left panel is
  calculated assuming a constant radiative efficiency
  $\epsilon_X=10^{-4} (\epsilon_{\rm bol}/0.1)$, while the right hand
  panel assumes $\epsilon_X= 0.01 (\epsilon_{\rm bol}/0.1)
  (\alpha/0.1) \epsilon_{rad} ( (\alpha/0.1) 0.1 \eddr) $, where
  $\epsilon_{\rm rad}$ is given by equation~\eqref{eq:efficiency} and
  $\eddr$ corresponds to the gas inflow rate on large scales.  Shown
  for comparison are the X-ray luminosities calculated for the maximum
  thermally-stable accretion rate ({\it dashed orange line};
  eq.~[\ref{eq:Mdotmax}]); the SN Ia-regulated accretion rate ({\it
    dashed teal line}; eq.~[\ref{eq:eddr_Ia}]), and the Compton
  heating-regulated accretion rate ({\it dashed pink line};
  eq.~[\ref{eq:MdotCa}]), again all calculated for the average SFH
  corresponding to each SMBH mass.}
\end{figure*}
